Spin canonical divisors of log stacky curves

### 2015-06-24 stacky_write_up/spin_cring.tex
minor fixes from Peter's merge

\begin{cor}
Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
\end{cor}
\begin{proof}
For a similar reason as in corollary \ref{cor:genus_0_posiive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
\end{proof}

@@

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
If $\sigma = (0; e_1, \ldots, e_r; 0)$ is not one of the
exceptional cases in Table ~\ref{table:g_0_exceptional} and $r \leq
5$, then $\sigma$ ``lies above'' one of the base cases of Lemma
~\ref{lem:g_0_admissible_cases}. In other words, one of the base
cases $(\sigma', J)$ with $\sigma' = (0; e_1', \ldots, e_r'; 0)$
satisfies the property that for all $i \in J$, $e_i \geq e_i'$ and
$e_i = e_i'$ otherwise. If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
this case satisfies all of the conditions by Lemma \todo{need this case
to satisfy conditions for adding points}, the
immediate consequence of parts (a) and (c) of Proposition
~\ref{prop:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
\ldots, e_r')$ with relations generated up to degree $2e$.
Furthermore, Proposition ~\ref{prop:sat_three_induction}(d)
implies that these cases satisfy all of the hypotheses of Theorem
~\ref{thm:ram_order_ind}.

>>>>

\begin{cor}
Let $D$ be a fractional $\frac{a}{b}$-canonical divisor of a genus 0 stacky curve with denominator $b > 2$ when $\frac{a}{b}$ is written in reduced form.
\end{cor}
\begin{proof}
For a similar reason as in corollary \ref{cor:genus_0_positive_delta}, $D$ must be equivalent to an effective divisor (in this case even when $\delta=0$), so by corollary \ref{cor:effective_Q_divisor_can_ring} we get the desired result.
\end{proof}

@@

Now suppose $\delta = 0$, so $\halfcan$ is not necessarily effective.
Let $\sigma = (0; e_1, \ldots, e_r; 0)$ be a signature with $r > 0$
and not one of the exceptional cases in Table
~\ref{table:g_0_exceptional}.

If $r > 5$, then we can use Lemma
~\ref{lem:sat_three_induction} to add ramified points with
ramification order $3$ to case (k) of Lemma
~\ref{lem:g_0_admissible_cases}, which corresponds to $\sigma_{11}
= (0; 3, 3, 3, 3, 3; 0), J_{11} = \{1, 2, 3, 4, 5\}$. Since
this case satisfies all of the conditions by Lemma \todo{need this case
to satisfy conditions for adding points}, the
immediate consequence of parts (a) and (c) of Lemma
~\ref{lem:sat_three_induction} is that any $R(\sx', \Delta,
\halfcan')$ corresponding to signatures $\sigma'$ with ramification
orders all equal to $3$ is generated up to degree $e := \max(5, e_1',
\ldots, e_r')$ with relations generated up to degree $2e$.
Furthermore, Lemma ~\ref{lem:sat_three_induction}(d)
implies that these cases satisfy all of the hypotheses of Theorem
~\ref{thm:ram_order_ind}.
